RADseq Works in Primates, Dammit.

### 2012-12-09 trunk/paper/paper.tex
Added sample list table to paper

@@

	Sequence reads were demultiplexed, or separated by barcode, and reads without an expected barcode or an intact restriction enzyme cut site were excluded from the analysis. Reads were then aligned to the rhesus macaque reference genome (v.1.0, Mmul_051212/rheMac2, \textcolor{red}{ref}) using BWA with default parameters. Reads that were unmapped, unpaired, duplicates, or that had low mapping quality were removed after alignment using Picard (\textcolor{red}{ref}) and BamTools (\textcolor{red}{ref}).

>>>>

\begin{table}[h]
\caption{Samples}
\begin{center}
  \begin{tabular}{ l | l | l }
    \hline
    Taxon & Source & Geographic Locality \\ \hline\hline
    \textcolor{red}{Langur?} & NYU Collection & Unknown \\ \hline
    \emph{Allenopithecus nigroviridis} & NYU Collection & Unknown \\ \hline
    \emph{Macaca mulatta} & NYU Collection & Unknown \\ \hline
    \emph{Cercocebus torquatus atys} & NYU Collection & Unknown \\ \hline
    \emph{Papio anubis\textcolor{red}{?}} & NYU Collection & Unknown \\ \hline
    \emph{Theropithecus gelada} & NYU Collection & Unknown \\ 
    \hline
  \end{tabular}
\end{center}
\end{table}

@@

	Sequence reads were demultiplexed, or separated by barcode, and reads without an expected barcode or an intact restriction enzyme cut site were excluded from the analysis. Reads were then aligned to the rhesus macaque reference genome (v.1.0, Mmul\_051212/rheMac2, \textcolor{red}{ref}) using BWA with default parameters. Reads that were unmapped, unpaired, duplicates, or that had low mapping quality were removed after alignment using Picard (\textcolor{red}{ref}) and BamTools (\textcolor{red}{ref}).
